Supporting information

### 2016-08-26 gm_pce/review_response.Rmd

---
title: "Response to referees"
author: "Court Campany"
date: "26 August 2016"
output: word_document
---

```{r, results='asis', echo=FALSE, warning=FALSE}
library(knitr)
opts_knit$set(root.dir = '../')
```

*Editor*

*Referee #1*

*Referee #2*

- 1. Wingate et al. 2007:

\
- 2. The measurements were taken as a closed system with the coupled TDl-Licor 6400, independent from the whole-tree chamber conditions. Additionally, specifically choosen CO~2~ cyclinders used for the Licor 6440 were closer to ambient air 13C (~ 10&permil) instead of standard CO~2~ which are fossil fuel derived (~ 30&permil). Thus the WTC atmosphere or CO~2~ cylinder $\delta$^13^C should not interfer with steady state conditions of the leaf measuremnts.

__Specific Comments:__
- line 358:We corrected the text to match stats from Table 2

- line 392: We agree that thermal acclimation is not previosuly discussed before this point is made. However, the experimental design does include a +3C warming treatment, and the potential affects of warming on leaf physiology are mentioned in the introduction. As there were very few effects of climate warming observed in this aspect of the experiment, we feel it is important to address a possible explaination for the lack of observed warming effects using published findings from this experiment.

- Q: Nitrogen concentration in the leaves had a weak postive relationship with measured rates of mesophyll conductance if all leaves were considered. This weak relationship disappeared if sun and shade leaves were analyzed seperately. Since we can only speculate about the effect of aquaporins we do not include gm v. N in the manuscript.

- line 404-415:

- line 412-415: *REMKO*

- Q: On average mesophyll conductance and stomatal might be expected to be correlated when investigating interspecific comparisions, such as in Flexas et al. 2013 (Figure 1). The dynamic responses of leaf physiolgy to environmental conditions within a species/canopy are likely to alter this relationship. In this experiment, you can see a strong postive relationship when only sun leaves are considered (which is commonly what most experiments report), similar to the Flexas paper. However, due to the unexpected stomatal behavior in shade leaves this relationship was reversed. We have attached a quick figure below for the referee, but have not included it in the manuscript as it can be inferred from Table 1 and Figure 3 if necessary.

\
```{r gmgs, fig.align='center', fig.width=5, fig.height=5, echo=FALSE,warning=FALSE,dev="png",message=FALSE, dpi=600}
source("master_scripts/gmgs_referee2.R")
```

### 2016-08-26 gm_pce/review_response.Rmd

---
title: "Response to referees"
author: "Court Campany"
date: "26 August 2016"
output: word_document
---

```{r, results='asis', echo=FALSE, warning=FALSE}
library(knitr)
opts_knit$set(root.dir = '../')
```

*Editor*
- 1. These leaves studied in this experiment juvenille leaves, as the *E. tereticornis* trees were grown for ~ 1 year. The fact that LMA was similar within the canopy may not be uncommon for this leaf type and has also been noted in Eucalpt plantations (Nouvellon et al. 2010, cited in discussion). However, we have expanded the discussion to address fixed vs variable contols of leaf physiolgy specific to LMA with additional citiations (see reply to Referee # 2 specific comments).

\
- 2. We feel that colors are necessary in this document to visualize leaf types (+light), while also showing temperature treatments.  It is near impossible to clearly distinguish all of these with symbols alone, and complicates visualization of confidence intervals on scatter plots.  We have attempted to tone-done the color palette, while also distguishing colors properly for color-blind readers.

\
- 3/4. After careful thought we have decided to move the information regarding parameters derived ACi curves to the supplement.  We only want to show that sun and shade leaves were fundamentaly different in their photosyntheitic capacity.  As such, we have decided to use this data to generate Amax values at a common C~i~ between the leaf types. This very simply shows the point we aim to make. If the derivation and representation of J~max~/V~cmax~ values has distracted the editor from this point, it is likely to also do so to other readers who are plant physiolgists. These two parameters will be reported in the supplementary as additional evidence supporting significant difference in photosynthetic capacity between leaf types.

*Remko*The fitaci package used here correctly estimates J~max~.

We also acknowledge that AC~i~ response curves were intitally conceived with the notion that g~m~ was small enough to be ignored,     which we now know to not be true.  We spent consideral time fitting AC~C~ curves that generated unrealistic V~cmax~ estimates of up to ~300 mumols m^-2^s^-1^. This will likely be a new issue for the plant physiolgy community as more g~m~ data are generated, and we hope are datasets will eventually help contribute to a solution.

\
-  5. depth of leaf ----  llyod paper appendix ---add to text as well

@@

*Referee #1*

- 1. This experiment was harvested in May 2014, shortly after our measurements ceased.  Therefore, the suggestion to make diurnal measuremnts is no longer possible.

\
- 2. Leaves used for gas exchange were sampled and then measured for midday water potentails. This is explained in the first sentence of the subsection "Leaf Nitrogen and hydraulic conductance" in the methods.  The method used here for measureing leaf hydraulic conductance is also one of the three methods described in Flexas et al. 2013, which compared the coordination of leaf hydraulic conductance and mesophyll conductance.

\
- 3. Due to Referee #1 concern over cuvette measured transpiration, water potentials and subsequent leaf K calculations, we re-examined the calculation and analyses in the manuscript.  Initially, leaf K was calculated with transpiration rates in shade leaves under low light conditions. As light was then increased in shade leaves and then transpiration re-measured, it is entirely possible that this change could have altered the water status of the leaf and thus subsequent water potential measurements (which we can not determine).  As such we feel that the only leaf K which can properly reported is that of sun leaves vs shade leaves under high light. The data and results in the manuscript now reflect this change. This new data allows us to address aspects of Flexas et al. 2013 (and others) mentioned above, but partially inhibits our ability to test optimization theories from Peltoniemi et al. 2012.

@@

*Referee #2*

- 1. Wingate et al. 2007:

\
- 2. The measurements were taken as a closed system with the coupled TDl-Licor 6400, independent from the whole-tree chamber conditions. Additionally, specifically choosen CO~2~ cyclinders used for the Licor 6440 were closer to ambient air 13C (~ 10&permil) instead of standard CO~2~ which are fossil fuel derived (~ 30&permil). Thus the WTC atmosphere or CO~2~ cylinder $\delta$^13^C should not interfer with steady state conditions of the leaf measuremnts.

__Specific Comments:__

\
- line 358:We corrected the text to match stats from Table 2

\
- line 392: We agree that thermal acclimation is not previosuly discussed before this point is made. However, the experimental design does include a +3C warming treatment, and the potential affects of warming on leaf physiology are mentioned in the introduction. As there were very few effects of climate warming observed in this aspect of the experiment, we feel it is important to address a possible explaination for the lack of observed warming effects using published findings from this experiment.

\
- Q: Nitrogen concentration in the leaves had a weak postive relationship with measured rates of mesophyll conductance if all leaves were considered. This weak relationship disappeared if sun and shade leaves were analyzed seperately. Since we can only speculate about the effect of aquaporins we have not added gm v. N in the manuscript.

\
- line 404-405:

\
- line 412-415: *REMKO*

\
- Q: On average mesophyll conductance and stomatal might be expected to be correlated when investigating interspecific comparisions, such as in Flexas et al. 2013 (Figure 1). The dynamic responses of leaf physiolgy to environmental conditions within a species/canopy are likely to alter this relationship. In this experiment, you can see a strong postive relationship when only sun leaves are considered (which is commonly what most experiments report), similar to the Flexas paper. However, due to the unexpected stomatal behavior in shade leaves this relationship was reversed. We have attached a quick figure below for the referee, but have not included it in the manuscript as it can be inferred from Table 1 and Figure 3 if necessary.

### 2016-08-29 gm_pce/manuscript_gmes.Rmd
started reviewer response RMD started edits in manuscript
new amax figure and results
aci moved to supp with methods and table....no figure

parfig <- "1"
acifig <- "2"
agmgsfig <- "3"
gebarfig <- "4"
waterusefig <- "5"
gmshadefig <- "6"
ciccfig <- "7"

airvarfig <- "S1"
deltafig <- "S2"
get1fig <- "S3"
get2fig <- "S4"

@@

##Photosynthetic capacity from A-*C*~i~ curves
Photosynthetic CO~2~ response (A-*C*~i~) curves were measured for one sun and shade leaf for each WTC in February 2014, when all trees were well-watered in each temperature treatment (*n*=6). Each A-*C*~i~ curve began at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l l^-1^ with leaf temperature (*T*~leaf~) held constant at 25 &deg;C, and saturating PPFD (1800 $\mu$mols m^-1^ s^-1^). From these curves the photosynthetic parameters, *J*~max~ and *V*~cmax~, were quantified using the photosynthesis model of Farquhar et al. [-@farquhar1980biochemical]. We used the 'fitaci' function in the 'plantecophys' package in R, see Duursma [-@duursma2015] for detailed description of the fitting methods. This method uses non-linear regression to estimate *J*~max~, *V*~cmax~ and *R*~dark~ simultaneously. Because there was considerable practical difficulty in fitting A-*C*~c~ curves, we report standard *C*~i~-based *J*~max~ and *V*~cmax~, which effectively include a mesophyll conductance component. When fitting the A-*C*~i~ curves, we calculated $\Gamma_{*}$ with the same methods as for *g*~m~, described above (the estimated value at 25&deg;C was 38.9 $\mu$mol mol^-1^), and the combined Michaelis-Menten coefficient (*K*~m~) was estimated from Medlyn et al. [-@medlyn2002temperature] (713.4 $\mu$mol mol^-1^ at 25&deg;C, using a *K*~c~ of 405 $\mu$mol mol^-1^, with an atmospheric pressure of 100 kPa). The temperature response parameters for *J*~max~, *V*~cmax~ and *K*~m~ are not relevant since *T*~leaf~ was kept constant at 25&deg;C.

@@

##Leaf resource distribution
Across six measurement campaigns over the 7 month period, PPFD was reduced on average by >75% in the shade (Figure `r parfig`). Leaf-specific hydraulic conductance (*K*~L~) was similar across sun and shade leaves (Table `r wtc3tab1`). This was because neither leaf water potentials ($\Psi_{pd}$ and $\Psi_L$, Table `r wtc3tab1`) nor transpiration rates (*E*~L~ , Table `r wtc3tab2`) differed between leaf types. Leaf *N*~a~ was approximately 20% higher in sun leaves compared to shade leaves (Table `r wtc3tab1`). Leaf mass per area (LMA) was not different between leaf types (Table `r wtc3tab1`). No effect of the warming treatment was detected on  PPFD, $\Psi_{pd}$, $\Psi_L$, *K*~L~, *E*~L~, *N*~a~ or LMA either within or across leaf types (P > 0.05).

##Photosynthetic capacity and leaf photosynthesis rates 
The photosynthetic parameters *J*~max~ and *V*~cmax~ were higher in sun compared to shade leaves (Table `r wtc3tab1`), as estimated from A-*C*~i~ curves measured at 25 &deg;C (Figure `r acifig`a). Within leaf types, no effect of the warming treatment was detected on either parameter. Among the sampled leaves, *V*~cmax~ was positively related to leaf *N*~a~ across leaf types and temperature treatments (P = 0.01, Figure `r acifig`b).

@@

\
Mean *g*~m~ was higher in sun compared to shade leaves (+27%) under their local light environment (P < 0.001). Following the increase in PPFD from low to high light on the same leaf, *g*~m~ values of shade leaves increased on average 55% after approximately 25 min (Figure `r gmshadefig`). These measured values of *g*~m~ for shade leaves at high light were also equivalent or greater than those of sun leaves (Table `r wtc3tab2`). Proportional increases in *g*~m~ were matched by proportional increases in *A*~n~ from low to high light in shade leaves (Figure `r gebarfig`b,c). Photosynthesis scaled positively with increases in *g*~m~ for all leaves, with similar intercepts but different slopes between leaf type and light treatment (P = 0.019). The large increases in *g*~m~ in shade leaves under high light likely resulted in the highest rates of *A*~n~ (Figure `r agmgsfig`b). No differences in *g*~m~ were detected with the warming treatment within leaf types. Mesophyll conductance did not vary across measurements campaigns within leaf types and light treatments (Figure `r get1fig`b), but a weak negative relationship with increasing leaf temperature was detected with sun and shade leaves under their local light environment (P = 0.001 for sun leaves, P = 0.04 for shade leaves).

@@

```{r, echo=FALSE}
resourcetab2 <- rbind(resourcetab, c("P value","", as.character(pval)))
greeks=c(alpha='\u03b1', Delta='\u0394', Sigma='\u03A3', mu='\u03bc',delta = '\u03b4')

dust(resourcetab2)%>%
  sprinkle_colnames("Leaf", "Temperature", "LMA", "*N*~a~", "*V*~cmax~", "*J*~max~","K",paste0("$\\Psi$","~pd~"),paste0("$\\Psi$","~L~"), paste0("$\\delta$","^13^C")) %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```

@@

```{r par, fig.width=7, fig.height=7, echo=FALSE,warning=FALSE,dev="png",message=FALSE, dpi=600, dev.args=list(type="cairo"), eval=includeFigs}

@@

```{r acicurves, fig.width=8, fig.height=10, warning=FALSE,echo=FALSE,dev="png", dpi=600,message=FALSE, dev.args=list(type="cairo"), eval=includeFigs}

@@

**Figure 2**. Photosynthetic capacity, photosynthesis rate and leaf nitrogen for sun and shade leaves. (a) A-*C*~i~ curves for sun and shade leaves grown under elevated (ET) and ambient (AT) temperature treatments. A-*C*~i~ curves were measured once on all trees, in February 2014, at 25°C and at saturating light (1800 $\mu$mols m^-1^ s^-1^). (b) The relationship between *V*~cmax~ and mean leaf N per area (*N*~a~) for each chamber, including sun leaves and shade leaves at low light. (c) The relationship between leaf net photosynthesis rate (*A*~n~) and leaf *N*~a~ for sun and shade leaves measured under their ambient light and temperature conditions. For (b,c) the dashed line represents the significant linear model fit for all leaves, with a marginal and conditional *R*^2^ of 0.28 and 0.35 for (b) and 0.24 and 0.33 for (c).

@@

```{r Agmgs, fig.width=7, fig.height=7, echo=FALSE,warning=FALSE,message=FALSE,dev="png", dpi=600, dev.args=list(type="cairo"), eval=includeFigs}

>>>>

parfig <- "1"
amaxfig <- "2"
agmgsfig <- "3"
gebarfig <- "4"
waterusefig <- "5"
gmshadefig <- "6"
ciccfig <- "7"

airvarfig <- "S1"
deltafig <- "S2"
get1fig <- "S3"
get2fig <- "S4"
acifig <- "S5"

@@

##Photosynthetic capacity from A-*C*~i~ curves
Photosynthetic CO~2~ response (A-*C*~i~) curves were measured for one sun and shade leaf for each WTC in February 2014, when all trees were well-watered in each temperature treatment (*n*=6). Each A-*C*~i~ curve began at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l l^-1^ with leaf temperature (*T*~leaf~) held constant at 25 &deg;C, and saturating PPFD (1800 $\mu$mols m^-1^ s^-1^). From these curves the photosynthetic capacity of each leaf (*A*~max~) was determined as the maximum rate of photosynthesis measured at the highest observed *C*~i~. The photosynthetic parameters, *J*~max~ and *V*~cmax~, were also generated from each A-*C*~i~ curve and their derivations are presented in Supporting Information Methods S2.

@@

##Leaf resource distribution
Across six measurement campaigns over the 7 month period, PPFD was reduced on average by >75% in the shade (Figure `r parfig`). Leaf *N*~a~ was approximately 20% higher in sun leaves compared to shade leaves (Table `r wtc3tab1`). Leaf mass per area (LMA) was not different between leaf types (Table `r wtc3tab1`).

*Leaf-specific hydraulic conductance (*K*~L~) was similar across sun and shade leaves (Table `r wtc3tab1`). This was because neither leaf water potentials ($\Psi_{pd}$ and $\Psi_L$, Table `r wtc3tab1`) nor transpiration rates (*E*~L~ , Table `r wtc3tab2`) differed between leaf types.*

 No effect of the warming treatment was detected on  PPFD, $\Psi_{pd}$, $\Psi_L$, *K*~L~, *E*~L~, *N*~a~ or LMA either within or across leaf types (P > 0.05).

##Photosynthetic capacity and leaf photosynthesis rates 
Mean photosynthetic capacity (*A*~max~) of sun leaves  was signifcantly higher (+27%, P = 0.001) compared to shade leaves, when measured at saturating light and 25 &deg;C. Within leaf types, no effect of the warming treatment was detected on *A*~max~. *A*~max~ was positively related to leaf *N*~a~ across leaf types and temperature treatments (P = 0.01, Figure `r amaxfig`). Similarily, the the photosynthetic parameters *J*~max~ and *V*~cmax~ were higher in sun compared to shade leaves (Supplementary Table 1).

@@

\
Mean *g*~m~ was higher in sun compared to shade leaves (+27%) under their local light environment (P < 0.001). Following the increase in PPFD from low to high light on the same leaf, *g*~m~ values of shade leaves increased on average 55% after approximately 25 min (Figure `r gmshadefig`). These measured values of *g*~m~ for shade leaves at high light were also indistinguishable than those of sun leaves (Table `r wtc3tab2`). Proportional increases in *g*~m~ were matched by proportional increases in *A*~n~ from low to high light in shade leaves (Figure `r gebarfig`b,c). Photosynthesis scaled positively with increases in *g*~m~ for all leaves, with similar intercepts but different slopes between leaf type and light treatment (P = 0.019). The large increases in *g*~m~ in shade leaves under high light likely resulted in the highest rates of *A*~n~ (Figure `r agmgsfig`b). No differences in *g*~m~ were detected with the warming treatment within leaf types. Mesophyll conductance did not vary across measurements campaigns within leaf types and light treatments (Figure `r get1fig`b), but a weak negative relationship with increasing leaf temperature was detected with sun and shade leaves under their local light environment (P = 0.001 for sun leaves, P = 0.04 for shade leaves).

@@

```{r, echo=FALSE}
resourcetab2 <- rbind(resourcetab[, c(1:4,7:10)], c("P value","", as.character(pval)))
greeks=c(alpha='\u03b1', Delta='\u0394', Sigma='\u03A3', mu='\u03bc',delta = '\u03b4')

dust(resourcetab2)%>%
  sprinkle_colnames("Leaf", "Temperature", "LMA", "*N*~a~", "K",paste0("$\\Psi$","~pd~"),paste0("$\\Psi$","~L~"),  paste0("$\\delta$","^13^C")) %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```

@@

```{r par, fig.width=7, fig.height=7, echo=FALSE,warning=FALSE,dev="png",message=FALSE, dpi=600, eval=includeFigs}

@@

```{r acicurves, fig.width=8, fig.height=10, warning=FALSE,echo=FALSE,dev="png", dpi=600,message=FALSE, eval=includeFigs}

@@

**Figure 2**. The relationship between mean leaf N per area (*N*~a~) for each chamber and photosynthetic capacity (*A*~max) for sun and shade leaves grown under elevated (ET) and ambient (AT) temperature treatments. *A*~max represents the net photosynthetic rate at the highest C~i~ values taken from A-*C*~i~ curves measured once on all trees, in February 2014, at 25°C and at saturating light (1800 $\mu$mols m^-1^ s^-1^). The dashed line represents the significant linear model fit for all leaves, with a marginal and conditional *R*^2^ of 0.59 and 0.62.

@@

```{r Agmgs, fig.width=7, fig.height=7, echo=FALSE,warning=FALSE,message=FALSE,dev="png", dpi=600, eval=includeFigs}

### 2016-08-29 gm_pce/manuscript_gmes_SuppInfo.Rmd
new amax figure and results
aci moved to supp with methods and table....no figure

@@

```{r airvars, fig.width=7, fig.height=8.8, echo=FALSE,warning=FALSE,dev="png", dpi=600,  eval=includeFigs, dev.args=list(type="cairo")}
source("master_scripts/air_vars.R")
```
\
**Figure S1**. Daily maximum and minimum temperature (a), daily maximum VPD (b) and total daily PPFD (c) for each chamber across the experiment duration.
\
```{r deltacica, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE,dev="png", dpi=600, eval=includeFigs, dev.args=list(type="cairo")}
source("master_scripts/delta_cica.R")
```  
\
**Figure S2**. Relationship between the observed discrimination of ^13^CO~2~ measured during photosynthesis ($\Delta_o$) and measured *C*~i~/*C*~a~ for sun leaves measured at high light and shade leaves measured at both low and high light. The solid line represents the theoretical line for C3 plants from Evans et al. [-@evans1986carbon].
\
```{r gasex_temp3, fig.width=7, fig.height=9, echo=FALSE,warning=FALSE,dev="png", dpi=600, dev.args=list(type="cairo"), eval=includeFigs}
source("master_scripts/gasex_temp3.R")
```  
\
**Figure S3**. Response of *A*~n~ (a), *g*~m~ (b) and *C*~i~-*C*~c~ to leaf temperature for sun leaves and shade leaves at low and high light. Shaded symbols represent each monthly measurement campaign. Solid lines, colored by leaf and light type, are fitted line for the relationship with each parameter and leaf temperature across all measurement campaigns. All parameters with no relationship are fitted with zero slope and the overall mean value for each treatment combination. Weak negative relationships with *g*~m~ and increasing leaf temperature were detected with sun and shade leaves under their local light environment (*R*^2^ = 0.16 and 0.08, respectively). 
\
```{r gasex_temp4, fig.width=7, fig.height=9, echo=FALSE,warning=FALSE,dev="png", dpi=600, dev.args=list(type="cairo"), eval=includeFigs}
source("master_scripts/gasex_temp4.R")
```  
\
**Figure S4**. Response of VPD (a), *g*~s~ (b) and *C*~a~-*C*~i~ to leaf temperature for sun leaves and shade leaves at low and high light. Shaded symbols represents each monthly measurement campaign. Solid lines, colored by leaf and light type, are fitted line for the relationship with each parameter and leaf temperature across all measurement campaigns. All parameters with no relationship are fitted with zero slope and the overall mean value for each treatment combination. Leaf VPD inside the gas exchange cuvette was positively correlated with increasing leaf temperature for sun leaves and shade leaves at low and high light (*R*^2^ = 0.73, 0.58 and 0.72, respectively).

@@

>>>>

## Tables
*jmax vcmax values*
**Table S1**. Leaf morphological and physiological traits of sun and shade leaves under ambient and elevated temperature treatments for *Eucalyptus tereticornis*. Values of *V*~cmax~ and *J*~max~ are treatment mean (&pm; 1 standard error) from A-*C*~i~ curves measured in each chamber at 25 &deg;C and saturating light. Different letters represent significant differences between leaf type and temperature treatments (based on a Tukey test). The P value represents the overall effect between each unique combination of leaf type and temperature treatment for each trait.

```{r, echo=FALSE}
resourcetab2 <- rbind(resourcetab[,c(1:2, 5:6)], c("P value","", as.character(pval_aci)))

dust(resourcetab2)%>%
  sprinkle_colnames("Leaf", "Temperature", "*V*~cmax~", "*J*~max~") %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```

@@

```{r airvars, fig.width=7, fig.height=8.8, echo=FALSE,warning=FALSE,dev="png", dpi=600,  eval=includeFigs}
source("master_scripts/air_vars.R")
```
\
**Figure S1**. Daily maximum and minimum temperature (a), daily maximum VPD (b) and total daily PPFD (c) for each chamber across the experiment duration.
\
```{r deltacica, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE,dev="png", dpi=600, eval=includeFigs}
source("master_scripts/delta_cica.R")
```  
\
**Figure S2**. Relationship between the observed discrimination of ^13^CO~2~ measured during photosynthesis ($\Delta_o$) and measured *C*~i~/*C*~a~ for sun leaves measured at high light and shade leaves measured at both low and high light. The solid line represents the theoretical line for C3 plants from Evans et al. [-@evans1986carbon].
\
```{r gasex_temp3, fig.width=7, fig.height=9, echo=FALSE,warning=FALSE,dev="png", dpi=600, eval=includeFigs}
source("master_scripts/gasex_temp3.R")
```  
\
**Figure S3**. Response of *A*~n~ (a), *g*~m~ (b) and *C*~i~-*C*~c~ to leaf temperature for sun leaves and shade leaves at low and high light. Shaded symbols represent each monthly measurement campaign. Solid lines, colored by leaf and light type, are fitted line for the relationship with each parameter and leaf temperature across all measurement campaigns. All parameters with no relationship are fitted with zero slope and the overall mean value for each treatment combination. Weak negative relationships with *g*~m~ and increasing leaf temperature were detected with sun and shade leaves under their local light environment (*R*^2^ = 0.16 and 0.08, respectively). 
\
```{r gasex_temp4, fig.width=7, fig.height=9, echo=FALSE,warning=FALSE,dev="png", dpi=600, eval=includeFigs}
source("master_scripts/gasex_temp4.R")
```  
\
**Figure S4**. Response of VPD (a), *g*~s~ (b) and *C*~a~-*C*~i~ to leaf temperature for sun leaves and shade leaves at low and high light. Shaded symbols represents each monthly measurement campaign. Solid lines, colored by leaf and light type, are fitted line for the relationship with each parameter and leaf temperature across all measurement campaigns. All parameters with no relationship are fitted with zero slope and the overall mean value for each treatment combination. Leaf VPD inside the gas exchange cuvette was positively correlated with increasing leaf temperature for sun leaves and shade leaves at low and high light (*R*^2^ = 0.73, 0.58 and 0.72, respectively).

<!-- \ -->
<!-- ```{r acicurves, fig.width=8, fig.height=10, warning=FALSE,echo=FALSE,dev="png", dpi=600,message=FALSE, eval=includeFigs} -->
<!--  source("master_scripts/aci_vcmaxnitro.R") -->
<!-- ``` -->
<!-- \ -->
<!-- **Figure S5**. Photosynthetic capacity, photosynthesis rate and leaf nitrogen for sun and shade leaves. (a) A-*C*~i~ curves for sun and shade leaves grown under elevated (ET) and ambient (AT) temperature treatments. A-*C*~i~ curves were measured once on all trees, in February 2014, at 25°C and at saturating light (1800 $\mu$mols m^-1^ s^-1^). (b) The relationship between *V*~cmax~ and mean leaf N per area (*N*~a~) for each chamber, including sun leaves and shade leaves at low light.  For (b) the dashed line represents the significant linear model fit for all leaves, with a marginal and conditional *R*^2^ of 0.28 and 0.35. -->

@@

##Methods S2

###Photosynthetic parameters from A-*C*~i~ curves
From each A-*C*~i~ curve the photosynthetic parameters, *J*~max~ and *V*~cmax~, were quantified using the photosynthesis model of Farquhar et al. [-@farquhar1980biochemical]. We used the 'fitaci' function in the 'plantecophys' package in R, see Duursma [-@duursma2015] for detailed description of the fitting methods. This method uses non-linear regression to estimate *J*~max~, *V*~cmax~ and *R*~dark~ simultaneously. Because there was considerable practical difficulty in fitting A-*C*~c~ curves, we report standard *C*~i~-based *J*~max~ and *V*~cmax~, which effectively include a mesophyll conductance component. When fitting the A-*C*~i~ curves, we calculated $\Gamma_{*}$ with the same methods as for *g*~m~, described above (the estimated value at 25&deg;C was 38.9 $\mu$mol mol^-1^), and the combined Michaelis-Menten coefficient (*K*~m~) was estimated from Medlyn et al. [-@medlyn2002temperature] (713.4 $\mu$mol mol^-1^ at 25&deg;C, using a *K*~c~ of 405 $\mu$mol mol^-1^, with an atmospheric pressure of 100 kPa). The temperature response parameters for *J*~max~, *V*~cmax~ and *K*~m~ are not relevant since *T*~leaf~ was kept constant at 25&deg;C.
